Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-04 edubots_surveys.Rnw
Clarify the purpose of the paper

% Maybe move it to a different place later
In the present work we aim to complement the aforementioned study with teacher attitudes; teachers are the ones that actually would need to implement, 
% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
\item{ RQ4 - What kind of interaction media features do teachers value the most? }

@@

We will try to answer these questions through the analysis of questions and answers in the two surveys.

>>>>

% Maybe move it to a different place later
In the present work we aim to complement the aforementioned study with an analysis of teacher attitudes; teachers are the ones that actually would need to use, 
% Antonio - 'deploy' instead implement? Since in Computer Sciences implement and program are synonyms...
% JJ - deployment would be done by the university or whoever publishes the system. Deployment and implementation are two different things, anyway
% Antonio - Ok, but what I said is that 'implement' is a synonym of 'program' in this scope, and we write both in the same sentence as different things.
% And deploy does not make sense in this context. I will simply say use - JJ
configure and maybe program chatbots. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
\item{ RQ4 - What kind of interaction media features do teachers value the most? }

@@

We will try to answer these questions through the analysis of questions and answers in the two surveys. Eventually, what we want to obtain is a series of recommendations to make a successful deployment of chatbot technologies (and, in some cases, general instant messaging applications) in higher education.
